{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-08-02 wacv_for_review.tex
WACV with Deep Features Added

\documentclass{bmvc2k}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

%% Enter your paper number here for the review copy
\bmvcreviewcopy{825}

\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for
  High-Speed, Object Tracking}

% Enter the paper's authors in order
% \addauthor{Name}{email/homepage}{INSTITUTION_CODE}
\addauthor{Susan Student}{http://www.vision.inst.ac.uk/~ss}{1}
\addauthor{Petra Prof}{http://www.vision.inst.ac.uk/~pp}{1}
\addauthor{Colin Collaborator}{colin@collaborators.com}{2}

% Enter the institutions
% \addinstitution{Name\\Address}
\addinstitution{
 The Vision Institute\\
 University of Borsetshire\\
 Wimbleham, UK
}
\addinstitution{
 Collaborators, Inc.\\
 123 Park Avenue,\\
 New York, USA
}

\runninghead{Student, Prof, Collaborator}{BMVC Author Guidelines}

% Any macro definitions you would like to include
% These are not defined in the style file, because they don't begin
% with \bmva, so they might conflict with the user's own macros.
% The \bmvaOneDot macro adds a full stop unless there is one in the
% text already.
\def\eg{\emph{e.g}\bmvaOneDot}
\def\Eg{\emph{E.g}\bmvaOneDot}
\def\etal{\emph{et al}\bmvaOneDot}

%-------------------------------------------------------------------------
% Document starts here
\begin{document}

\maketitle

@@

@@

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
\caption{Examples of tracking results (yellow rectangles) by the
  proposed method on the ``UAV123'' dataset. This ``UAV123'' dataset
  is challenging for object tracking as a target's scale is changed
  drastically in a few frames.}
\label{ResultsIntroduction}
\end{figure*}

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, Zhang and his colleagues use the MOSSE tracker to estimate
a target's translation. And then they attempted to update the scale of
the target by further analyzing image, sub-regions with high
confidence. This is based on an assumption that the scale of a target
would not change much over two consecutive frames. Similarly, Ma and
his colleagues used two KCFs to learn the translation and scale of a
target separately \cite{ma2015long}. In particular, a KCF is used to
learn the translation of the target and its background. Given this,
another KCF is used to learn the target area to estimate a new scale
of the target. However, because of running more than a KCF on each
frame, this method degrades its run-time performance (i.e., $\leq 50
fps$). Our method is motivated by this idea -- the idea of deploying
multiple KCFs to address the issues of single target tracking: scale
and translation, but in a more efficient way. Figure \ref{Workflows}
illustrates the work-flow of the {\it E}nKCF. In particular, to
maximize run-time performance and accuracy, instead of running them
all together on every frame, we deploy three KCFs in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). By doing so, our method aims at addressing a scale
change and estimate target's motion efficiently while maintaining or
increasing run-time performance. Figure \ref{fig:Filters} shows
examples of the region of interest (ROI) associated with $R_{t}^{S}$,
$R_{t}^{L}$, and $R_{s}$.
\begin{figure}[!t]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
\end{tabular}
\caption{The work-flow of {\it E}nKCF tracking algorithm. We show the
  first seven frames of tracking where the first frame is the
  initialization frame. Afterward, the order of deploying three KCFs
  is repeating.}
\label{Workflows}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=1.0\textwidth]{figures/Filters_Details.pdf}
\caption{Examples of three filters; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}
The contribution of this study is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps that deploys an
ensemble of KCFs, in turn, to more effectively address the scale
variance and the dynamic maneuver of a target while preserving
run-time performance as high as possible. To minimize any potential
performance gap from transiting one KCF to another, we use a Bayes
filter.

@@

\begin{algorithm}[h]
\small
\DontPrintSemicolon
\KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, complete cycle of scale filter $n = 5$,}
\KwOut{	\uIf{$fc\:\%\:n=0$ (\textbf{Condition 1})}
			{
				Estimated Target State $(x_{t},y_{t},s_{t})$,
				Scale filter (\textit{target-only}) model $R_{s}$
			}
			 \ElseIf{$fc\:\%\:n>0\:\:and\:\:fc\:\%\:n\leq n/2$ (\textbf{Condition 2})}
			 {
				Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
			  	Large Area Translation Filter model $R_{t}^{L}$
			}			 
			 \Else (\textit{\textbf{Condition 3}})
			{			 
				 Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
				Small Area Translation Filter model $R_{t}^{S}$			
			}	
		}
\SetKwBlock{Begin}{function}{end function}
\Begin($\text{track($x_{t-1},y_{t-1},s_{t-1}$) }$)
{
 	// \textit{Translation Estimation - Particle Filter} \\
	Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $\mathbf{(x_{t},y_{t},s_{t-1})}$ \\
     // \textit{Translation Estimation - Correlation Filter} \\
	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position as $\mathbf{(x_{t},y_{t})}$ = $\mathbf{\textit{max}(y_{R_{t}})}$\\
	// \textit{Scale Estimation - Correlation Filter}\\
	Scale pool for $R_{s}$ : $S = \lbrace1.05,1.0,1/1.05\rbrace$,\\
	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{\textit{argmax}}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\ 
	Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ ($\mathbf{s_{t}}$=$\mathbf{s_{t-1}}$)\\
	// \textit{Update Translation - Particle Filter}\\
	Do Importance Re-sampling (if necessary) and compute the 
	mean of posterior pdf $\mathbf{(x_{t},y_{t})}$\\
	// \textit{Model Update}\\
	Update $R_{t}^{S}$,\\
	Update $R_{t}^{L}$\\
	\uIf{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}{
		Update $R_{s}$ (Condition 1)}
  \label{endfor}
  \Return{($x_{t},y_{t},s_{t}$)}
}
\caption{{\it E}nKCF Tracking Algorithm}\label{alg:MKCF}
\end{algorithm}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=1\textwidth]{figures/LearnedFiltersComparison2.pdf}
\caption{This figure shows that there is a marginal difference among
  the scale filters learned either at every frame or at every 5
  frames. The sub-figures at the the left show the scale filters
  trained at every frame and those at the right show the scale filters
  trained at every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure}

@@

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate metrics to compare the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high},
MOSSE \cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast} and ones in relatively
lower-speed ($\geq$50): SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ at 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny\quad\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_otb100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we removed
the particle filter. The method at the $2^{nd}$ column fliped the
order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
every frame in the listed order. The methods at the $7^{th}$ and
$8^{th}$ columns ran a translation and a scale filter on every frame
which is very similar to the way the LCT tracker \cite{ma2015long}
runs. To be precise, the LCT tracker comes with a re-detection method
for a long-term tracking. In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
at every frame, but this combination wills sacrifice run-time
performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
final translation estimation given by $R_{t}^{S}$ to update the scale.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset. This table empirically supported the usefulness of
  combining multiple KCFs as long as the deployment order is optimal.}
\label{table:Comparison_to_LCT}
\end{table}

@@

\textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
shows the results on the OTB100 dataset. Same as with UAV123 dataset,
we observed a similar performance. In particular, {\it E}nKCF showed a
good performance for handling the scale changes. It was the third best
and the second fastest tracking algorithm. For the precision metric,
{\it E}nKCF performed slightly better than most of tracking algorithms
in high-speed trackers. Interestingly, it outperformed another
correlation filter based tracker, DSST, but performing $5\%$ behind of
another low-speed scale adaptive SAMF tracker.
%\begin{figure}[!h]
%\centering
%\begin{tabular}{ccc}
%\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Precision_OTB100.eps}}
%\bmvaHangBox{\includegraphics[width=3.80cm]{./figures/Success_OTB100.eps}}\\
%\end{tabular}
%\caption{Comparison of {\it E}nKCF's performance with those of the
%  state-of-the-art tracking algorithms on the OTB100 dataset.}
%\label{fig:OTB100_DATASET}
%\end{figure}

@@

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123_10fps.eps}}
\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_uav123_10fps.eps}}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
  dataset where the original UAV123 data was temporally downsampled.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

@@

As future work, we investigate a way of re-initializing a target when
the target is lost, due to occlusion, illumination change, drastic
camera motion, etc.
%--------------
%\section*{Acknowledgements}
%put stuff here for the accepted , but not the ICCV version

\bibliography{draft}
\end{document}

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{wacv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%\wacvfinalcopy % *** Uncomment this line for the final submission

\def\wacvPaperID{****} % *** Enter the wacv Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifwacvfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}

%%%%%%%%% TITLE
\title{{\it E}nKCF: Ensemble of Kernelized Correlation Filters for
  High-Speed, Object Tracking}

% Authors at the same institution
%\author{First Author \hspace{2cm} Second Author \\
%Institution1\\
%{\tt\small firstauthor@i1.org}
%}
% Authors at different institutions
\author{First Author \\
Institution1\\
{\tt\small firstauthor@i1.org}
\and
Second Author \\
Institution2\\
{\tt\small secondauthor@i2.org}
}

\maketitle
\ifwacvfinal\thispagestyle{empty}\fi

@@

\begin{figure*}[!h]
\centering
\includegraphics[width=\textwidth]{./figures/ResultsIntroduction.pdf}
\caption{Examples of tracking results (yellow rectangles) by the
  proposed method on the ``UAV123'' dataset. This ``UAV123'' dataset
  is challenging for object tracking as a target's scale is changed
  drastically in a few frames.}
\label{ResultsIntroduction}
\end{figure*}

@@

\begin{figure*}[!h]
\centering
\begin{tabular}{cc}
\includegraphics[width=14.00cm]{./figures/Workflow_MKCF+PF.pdf}\\
\end{tabular}
\caption{The work-flow of {\it E}nKCF tracking algorithm. We show the
  first seven frames of tracking where the first frame is the
  initialization frame. Afterward, the order of deploying three KCFs
  is repeating.}
\label{Workflows}
\end{figure*}

@@

\begin{figure*}[!h]
\centering
\includegraphics[width=0.70\textwidth]{./figures/Filters_Details.pdf}
\caption{Examples of three filters; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure*}

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, Zhang and his colleagues use the MOSSE tracker to estimate
a target's translation. And then they attempted to update the scale of
the target by further analyzing image, sub-regions with high
confidence. This is based on an assumption that the scale of a target
would not change much over two consecutive frames. Similarly, Ma and
his colleagues used two KCFs to learn the translation and scale of a
target separately \cite{ma2015long}. In particular, a KCF is used to
learn the translation of the target and its background. Given this,
another KCF is used to learn the target area to estimate a new scale
of the target. However, because of running more than a KCF on each
frame, this method degrades its run-time performance (i.e., $\leq 50
fps$). Our method is motivated by this idea -- the idea of deploying
multiple KCFs to address the issues of single target tracking: scale
and translation, but in a more efficient way. Figure \ref{Workflows}
illustrates the work-flow of the {\it E}nKCF. In particular, to
maximize run-time performance and accuracy, instead of running them
all together on every frame, we deploy three KCFs in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). By doing so, our method aims at addressing a scale
change and estimate target's motion efficiently while maintaining or
increasing run-time performance. Figure \ref{fig:Filters} shows
examples of the region of interest (ROI) associated with $R_{t}^{S}$,
$R_{t}^{L}$, and $R_{s}$.

The contribution of this study is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps that deploys an
ensemble of KCFs, in turn, to more effectively address the scale
variance and the dynamic maneuver of a target while preserving
run-time performance as high as possible. To minimize any potential
performance gap from transiting one KCF to another, we use a Bayes
filter.

@@

\begin{algorithm*}[h]
\small
\DontPrintSemicolon
\KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, complete cycle of scale filter $n = 5$,}
\KwOut{	\uIf{$fc\:\%\:n=0$ (\textbf{Condition 1})}
			{
				Estimated Target State $(x_{t},y_{t},s_{t})$,
				Scale filter (\textit{target-only}) model $R_{s}$
			}
			 \ElseIf{$fc\:\%\:n>0\:\:and\:\:fc\:\%\:n\leq n/2$ (\textbf{Condition 2})}
			 {
				Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
			  	Large Area Translation Filter model $R_{t}^{L}$
			}			 
			 \Else (\textit{\textbf{Condition 3}})
			{			 
				 Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
				Small Area Translation Filter model $R_{t}^{S}$			
			}	
		}
\SetKwBlock{Begin}{function}{end function}
\Begin($\text{track($x_{t-1},y_{t-1},s_{t-1}$) }$)
{
 	// \textit{Translation Estimation - Particle Filter} \\
	Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $\mathbf{(x_{t},y_{t},s_{t-1})}$ \\
     // \textit{Translation Estimation - Correlation Filter} \\
	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position as $\mathbf{(x_{t},y_{t})}$ = $\mathbf{\textit{max}(y_{R_{t}})}$\\
	// \textit{Scale Estimation - Correlation Filter}\\
	Scale pool for $R_{s}$ : $S = \lbrace1.05,1.0,1/1.05\rbrace$,\\
	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{\textit{argmax}}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\ 
	Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ ($\mathbf{s_{t}}$=$\mathbf{s_{t-1}}$)\\
	// \textit{Update Translation - Particle Filter}\\
	Do Importance Re-sampling (if necessary) and compute the 
	mean of posterior pdf $\mathbf{(x_{t},y_{t})}$\\
	// \textit{Model Update}\\
	Update $R_{t}^{S}$,\\
	Update $R_{t}^{L}$\\
	\uIf{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}{
		Update $R_{s}$ (Condition 1)}
  \label{endfor}
  \Return{($x_{t},y_{t},s_{t}$)}
}
\caption{{\it E}nKCF Tracking Algorithm}\label{alg:MKCF}
\end{algorithm*}

@@

\begin{figure*}[!h]
\centering
\includegraphics[width=1\textwidth]{./figures/LearnedFiltersComparison2.pdf}
\caption{This figure shows that there is a marginal difference among
  the scale filters learned either at every frame or at every 5
  frames. The sub-figures at the the left show the scale filters
  trained at every frame and those at the right show the scale filters
  trained at every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure*}

@@

\begin{figure*}[h]
\centering
\begin{tabular}{ccc}
\tiny\quad\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
\includegraphics[width=3.30cm]{./figures/pr_uav123.eps}
\includegraphics[width=3.55cm]{./figures/sr_uav123.eps}
\includegraphics[width=3.30cm]{./figures/pr_otb100.eps}
\includegraphics[width=3.55cm]{./figures/sr_otb100.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure*}

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate metrics to compare the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high},
MOSSE \cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast} and ones in relatively
lower-speed ($\geq$50): SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ at 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we removed
the particle filter. The method at the $2^{nd}$ column fliped the
order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
every frame in the listed order. The methods at the $7^{th}$ and
$8^{th}$ columns ran a translation and a scale filter on every frame
which is very similar to the way the LCT tracker \cite{ma2015long}
runs. To be precise, the LCT tracker comes with a re-detection method
for a long-term tracking. In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
at every frame, but this combination wills sacrifice run-time
performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
final translation estimation given by $R_{t}^{S}$ to update the scale.
\begin{table*}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset. This table empirically supported the usefulness of
  combining multiple KCFs as long as the deployment order is optimal.}
\label{table:Comparison_to_LCT}
\end{table*}

@@

\textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
shows the results on the OTB100 dataset. Same as with UAV123 dataset,
we observed a similar performance. In particular, {\it E}nKCF showed a
good performance for handling the scale changes. It was the third best
and the second fastest tracking algorithm. For the precision metric,
{\it E}nKCF performed slightly better than most of tracking algorithms
in high-speed trackers. Interestingly, it outperformed another
correlation filter based tracker, DSST, but performing $5\%$ behind of
another low-speed scale adaptive SAMF tracker.

\textbf{Deep Learning Features} Our focus so far was to build a high speed tracker
that can run about 30fps on a low-end hardware. In this direction, we used HoG and
color features in an efficient way in the proposed {\it E}nKCF tracking concept. Deep Learning
features, on the other hand, recently have been proved to boost tracking accuracy \cite{ma2015hierarchical,
danelljan2015convolutional}. For this reason, we believe that, the {\it E}nKCF tracker can run more reliably with deep learning
features on the more sophisticated platforms (GPUs). \cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer features of the VGGNet \cite{simonyan2014very}. Their experiments showed that
the first convolutional layer features lead to slightly better precision and success rates than the second
layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper features. Their method employs the third convolutional layer
features to get the response map. In the next stage, they use the translation estimation from the first stage to
employ second convolutional layer features. Finally, the first convolutional layer features is extracted from the 
position estimated in the second stage. This coarse-to-fine position estimation approach allows embedding 
more representative features of the object. However, such approach requires multiple runs of a KCF at a single
frame, increasing the run-time complexity. For this reason, we follow a similar approach to \cite{danelljan2015convolutional} to embed
deep learning features.

Our {\it E}nKCF framework provides us flexibility to exploit different feature representations. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, 
considers at more than twice larger area than $R_{s}$. Taking this into account, we can assign deeper feature encodings to $R_{s}$ as it requires less
spatial information than  $R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the fourth convolutional layer features ($26\times26\times128$) to $R_{s}$  whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of the second layer features ($109\times109\times64$). This feature assignment is represented as  \textit{conv224-VGG}. Additionally, we assign the second convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and $R_{t}^{S}$ and compare this setting  (\textit{conv222-VGG}) to  \textit{conv224-VGG}. We use the VGGNet as it provides higher spatial resolution at the first layers than than AlexNet \cite{krizhevsky2012imagenet}.

As shown in fig.~\ref{fig:UAV123_DATASET_DeepFeatures}, both settings of the deep features outperform the HoG and color features as proposed in {\it E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in success rates (AUC). On the other hand, the \textit{conv224-VGG} setting performs slightly better than  \textit{conv222-VGG} in precision while achieving similar success rate (AUC).

\begin{figure}[h]
\begin{tabular}{ccc}
\tiny\quad\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.50cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

%\begin{figure}[!h]
%\centering
%\begin{tabular}{ccc}
%\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Precision_OTB100.eps}}
%\bmvaHangBox{\includegraphics[width=3.80cm]{./figures/Success_OTB100.eps}}\\
%\end{tabular}
%\caption{Comparison of {\it E}nKCF's performance with those of the
%  state-of-the-art tracking algorithms on the OTB100 dataset.}
%\label{fig:OTB100_DATASET}
%\end{figure}

@@

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
  dataset where the original UAV123 data was temporally downsampled.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

@@

As future work, we investigate a way of re-initializing a target when
the target is lost, due to occlusion, illumination change, drastic
camera motion, etc.

{\small
\bibliographystyle{ieee}
\bibliography{draft}
}

\end{document}
